---
Title: Statistical Inference Project Part-2
AUTHOR: REDY
datEE: 20/10/2020
OTPUT: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Part 1: BASIC INFERENTIAL ANALYSES

## INFO

```{r, warning=FALSE,message=FALSE}
library(dplyr)
library(ggplot2)
library(stats)

```

### KLEJCEOD3

#### SummarISATION

```{r, warning=FALSE,message=FALSE}
datsetfrmRpckge<-ToothGrowth
other<-summary(datsetfrmRpckge)
other
coal<-datsetfrmRpckge
harry<-str(coal)
```


### Load  dataa and perform some ANALYSES
here we put the dataa and do some exploratory analyses


#### SSHORPUT OUTPUT
a. AA ante amalauram aaa h anhaa puram i e ichapuram neela gtii laagutaru aandhra janam.
b. naatho vastaava naato vstaava naa pranam anthaa neek iste naato vastaava.



### 3.peodhhxneo exjepx ohiexnllx

```{r, warning=FALSE,message=FALSE}
opdatstges<-datsetfrmRpckge %>% group_by(supp,dose) %>% summarize(mnofhght=mean(len),dsofhgt=sd(len),chahl=n())
opdatstges$lallu <- with(opdatstges,mnofhght-dsofhgt/sqrt(chahl)*qt(0.975,df=chahl-1))
opdatstges$kanchna <- with(opdatstges,mnofhght+dsofhgt/sqrt(chahl)*qt(0.975,df=chahl-1))
print(opdatstges[,c(1,2,6,7)])
```

 ANSWER OPUT 95%. 

### 4 CONCLUSIONS
ADCHADHU PDU DAQUIT PANNUDA AHA PODUA VANDA .VANDHATA LE VADHATAA LE.



